### 2020-06-01 paper.tex
Add an Extra Citation to the References Section
Add Related Work Section Introduction

Insert related work here

@@

>>>>

As already stated, the placement problem is an NP-complete problem where its optimum solution can be found by trying all possible cells configurations, but due to the tremendous number of cells that exist in almost all VLSI designs which range from millions to billions of cells, it would be utterly impractical to compute every possible configuration in order to find the fittest one. Because of this nature, previous literature made significant improvements in terms of solution fitness and the amount of time consumed through using heuristic techniques such as simulated annealing used in \cite{b7}, \cite{b10}, \cite{b11}, \cite{b12}, \cite{b13} and \cite{b14}, min-cut placement algorithm used in \cite{b1} and \cite{b15} and genetic algorithms used in \cite{b2}, \cite{b3} and \cite{b7}. However, optimizing placement algorithms isn't limited to heuristic approaches only as others have used different approaches to achieve solid results. For instance, Natarajan et al \cite{b8} used an analytical placement algorithm that is based on the quadratic placement approach.

@@

\bibitem{b16} Shahookar, K. and Mazumder, ``VLSI cell placement techniques'', \textit{ACM Computing Surveys}, vol. 23, no. 2, pp. 145-220.
